Software Citation Principles

### 2016-04-19 sc-principles/software-citation-principles.tex
added explanation of use cases prereq, addressing issue #130

@@

\subsection{Unique identification}

@@

\subsection{Access to software}

>>>>

All use cases assume the existence of a citable software object, typically created by the authors\slash developers of the software.
Developers can achieve this by, e.g., uploading a software release to Figshare or Zenodo~\cite{github-citable-code-guide} to obtain a DOI.
Necessary metadata should then be included in a \texttt{CITATION} file~\cite{ssi-citation-files} or machine-readable \texttt{CITATION.jsonld} file~\cite{transitive_credit_json-ld}.
When software is not freely available (e.g., commercial software), alternative means may be used to create citable objects via identifiers such as RRIDs, although these topics are discussed more in \S\ref{sec:identification} and \S\ref{sec:access}.

@@

\subsection{Unique identification}
\label{sec:identification}

@@

\subsection{Access to software}
\label{sec:access}
